Make any stupid plot you want

### 2021-02-19 draft/sections/implementation.tex
stripping out draw non used args + adding axes argument to view

    def draw(self, renderer, *args, **kwargs):
        # returns K, indexed on fiber then key 
        # is passed the 
        view = self.data.view(self.axes) 
        # visual channel encoding applied fiberwise 
        visual = {p: encoder(view[f] if f is not None else None) 
                     for p, (f, encoder) in self.transforms.items()}
        self.assemble(visual)
        # pass configurations off to the renderer
        super().draw(renderer, *args, **kwargs)
\end{minted}

>>>>

    def draw(self, renderer):
        # returns K, indexed on fiber then key 
        # is passed the 
        view = self.data.view(self.axes) 
        # visual channel encoding applied fiberwise 
        visual = {p: encoder(view[f] if f is not None else None) 
                     for p, (f, encoder) in self.transforms.items()}
        self.assemble(visual)
        # pass configurations off to the renderer
        super().draw(renderer)
\end{minted}
